Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
tidy
silly crashing...

Multilayer networks represent a novel framework for explicitly scale on the
influence of habitat selection and space use on sociality. Animal social systems
can be parsed by spatial contexts, defined, for example, by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of land cover spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Figure
S1)<!--TODO-->. Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Forage and open
layers had greater individual variation in graph strength, while forage was the
sole layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

@@

Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviours. Despite animals selecting for different landscape attributes
at different scales [@Mayor_2009], the use of multiscale analyses for habitat
selection is still critically lacking [@McGarigal_2016].

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougar
(*Puma concolor*) home ranges overlapped more in regions with high hunting
opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
tarandus*) sociality differed between seasons, where social associations were
stronger in winter and contrastingly low in summer when resource availability
are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
habitat selection in larger groups and avoidance of predation risk was a main
factor contributing to their habitat selection [@Fortin_2009]. These examples,
comparing sociality and habitat selection across temporal or spatial contexts,
are implicitly multilayer analyses.

@@

## Etc
<!-- soc -->
Social scale is a major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015]. With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the winter,
individuals demonstrate dramatically different graph strength (Figure 
\@ref(fig:socres)) in different habitat types, having higher graph strength in
forage and open habitats where they can likely see each other and still interact
with visual cues unlike in forest habitats. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca
mulatta*) had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences. Multilayer networks provide the opportunity to
address these types of questions involving social scale with all the individual
layers of interaction integrated in a holistic way.

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
networks in the emerging integration of social and spatial ecology within the
behavioural ecology literature.

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Multilayer networks
provide a way to bridge these different scales so that we can examine social
phenotypes in more holistic ways rather than looking at each scale separately as
has traditionally been done. From a monolayer network perspective, social
phenotypes are increasingly linked to important fitness for individuals of
various species, including primates [@Brent_2017; @Thompson_2019], dolphins
[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
social scales, types of interactions, and temporal, seasons and stages of life,
have emerged as important for understanding fitness consequences in the context
of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011].

>>>>

Multilayer networks represents a novel framework for explicitly testing the
influence of habitat selection on sociality across scales. Animal social systems
can be parsed by spatial contexts, defined by habitat types as in
Figure \@ref(fig:lcres). Given that habitat data are available across a wide
range of spatial scales, we evaluated the influence of habitat spatial
resolution on multilayer network metrics. The results indicate varied influence
of increasing spatial resolution depending on the habitat layer. As spatial
resolution increased, edge overlap decreased in forage while remaining stable in
open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
of relocations in this habitat type with increasing spatial resolution (Figure
S1)<!--TODO-->. Similar to increasing spatial distance threshold, the influence
of increasing spatial resolution on graph strength was notably different between
habitat layers. Forest layers showed little change in graph strength with
increasing spatial resolution and variation between individuals. Forage and open
layers had greater individual variation in graph strength, while forage was the
sole layer to show large responses in graph strength to increasing spatial
resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
related to habitat are explicitly dependent on spatial scale. Edge overlap can
indicate if some associations between individuals are dependent on the
habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
are insufficient to capture rare habitats, context-specific relationships
between individuals may not be captured by multilayer networks.

@@

@@

## Etc
The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
networks in the emerging integration of social and spatial ecology within the
behavioural ecology literature.
